% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Liang Yu}

\basicInfo{
  \email{liang.j.yu@gmail.com} \textperiodcentered\ 
  \phone{(714) 248-5264} \textperiodcentered\ 
  \linkedin[liang-j-yu]{https://www.linkedin.com/in/liang-j-yu}
  \github[MisterYu]{https://www.github.com/MisterYu}}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Jet Propulsion Laboratory} Pasadena, CA}{Oct 2017 -- Jan 2018}
\role{Software Engineer}{}
Developer (under contract) in the Machine Learning and Instrument Autonomy group.
\begin{itemize}
  \item Devised test cases and developed test code in C and Python for existing machine learning code bases.
  \item Deployed tests in a Jenkins continuous integration environment.
\end{itemize}

\datedsubsection{\textbf{Jet Propulsion Laboratory} Pasadena, CA}{Aug 2016 -- May 2017}
\role{Software Engineer}{}
Developer (under contract) on a team supporting a synthetic image generation pipeline.
\begin{itemize}
  \item Created and profiled production-level, multithreaded Python tools for image generation, image processing, and workflow acceleration in an agile environment.
\end{itemize}

\datedsubsection{\textbf{xxx Projects}}{Jan. 2015 -- Present}
\role{C, Python, Django, Linux}{Individual Projects, collaborated with xxx}
Brief introduction: xxx
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\datedsubsection{\textbf{\LaTeX\ résumé template}}{May. 2015 -- Present}
\role{\LaTeX, Maintainer}{Individual Projects}
An elegant \LaTeX\ résumé template, https://github.com/billryan/resume
\begin{itemize}
  \item Easy to be further customized or extended
  \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
  \item FontAwesome 4.5.0 support
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C == Python > C++ > Java
  \item Platform: Linux
  \item Development: Web, xxx
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Souther California (USC)}, Los Angeles}{2003 -- 2005}
\textit{M.S.} in Electrical Engineering (EE)
\datedsubsection{\textbf{University California, Los Angeles (UCLA)}, Los Angeles}{1998 -- 2002}
\textit{B.S.} in Electrical Engineering (EE)

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
\datedline{Other awards}{2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://your.blog.me
  \item GitHub: https://github.com/username
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
